Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-19 paper/intro.tex
checkpointing; outlined remainder of semantics section

Two security-enhancing transformations are discussed in the remainder
of the paper: (1) the insertion of a filter to prevent malformed data
from a malicious actor from being propagated to downstream components,
and (2) the insertion of a monitor to detect (and alert) unexpected
behaviors arising from untrusted components. These transformations not
only change the architecture of the model by adding in new components;
they also generate a formal specification for the behavior of the
inserted high-assurance components in the AGREE language. Those
specifications are sufficient for model checking to prove that---due
to the newly included high-assurance components---the hardened
system meets its cyber-resiliency requirements.

>>>>

Two security-enhancing transformations are discussed: (1) the
insertion of a filter to prevent malformed data from a malicious actor
from being propagated to downstream components, and (2) the insertion
of a monitor to detect (and alert) unexpected behaviors arising from
untrusted components. These transformations not only change the
architecture of the model by adding in new components; they also
generate a formal specification for the behavior of the inserted
high-assurance components in the AGREE language. Those specifications
are sufficient for model checking to prove that---due to the newly
included high-assurance components---the hardened system meets its
cyber-resiliency requirements.

### 2022-03-19 paper/semantics.tex
checkpointing; outlined remainder of semantics section

There is a conditional, $\itelse{b}{(-)}{(-)}$, for both terms and
formulas. There are also temporal operators $\konst{pre}(-)$, delay
$(-) \to (-)$, and $\konst{Historically}(-)$.

@@

>>>>

There is a conditional, $\itelse{b}{(-)}{(-)}$, for both terms and
formulas. There are also temporal operators $\konst{pre}(-)$, delay
$(-) \to (-)$, and $\konst{Hist}(-)$.

@@

The temporal operators deal with time in more significant ways:
\[
\begin{array}{rcl}
\sem{\konst{pre}(e)}_t & = & \sem{e}_{t-1}, \mathrm{when}\ t > 0 \\
\sem{e_1 \to e_2}_t & = & \itelse{t=0}{\sem{e_1}_0}{\sem{e_2}_t} \\
\sem{\konst{Hist}(b)}_t & = & \forall n \leq t.\; \sem{b}_n
\end{array}
\]

\subsubsection{Extracting computation from specification}

A subtle aspect of our approach is that AGREE does not explicitly
present the computation that a component performs. This is entirely
appropriate since AGREE is intended to reason about components solely
at the specification level. However, specifications do support state
variables, and updates to them; consequently---for inserted leaf-level
security components---SPLAT interprets sequences of variable
assignments as specifying the computation of the component.

\begin{itemize}
\item \textit{Point to discussion on output code guarantees}

\item \textit{code contract representation}

\item \textit{strmStep}

\item \textit{Contract semantics}

\item \textit{How example looks}
\end{itemize}

### 2022-03-19 paper/sw-contract.tex
checkpointing; outlined remainder of semantics section

\newsavebox{\sw}
\begin{lrbox}{\sw}
\begin{lstlisting}[style=agree,numbers=left]
eq req : bool = event(AutomationRequest);*\label{line:sw-event-def-start}*
eq avl : bool = event(AirVehicleLocation);
eq wp : bool = event(Waypoint);
eq strt: bool = event(Start);
eq alrt : bool = event(Alert);*\label{line:sw-event-def-end}*

>>>>

\newsavebox{\sw}
\begin{lrbox}{\sw}
\begin{lstlisting}[style=agree,numbers=left]
eq req : bool = event(AutomationRequest);*\label{line:sw-event-def-start}*
eq avl : bool = event(AirVehicleLocation);
eq wp  : bool = event(Waypoint);
eq strt: bool = event(Start);
eq alrt: bool = event(Alert);*\label{line:sw-event-def-end}*
